\section{Discussion}
\paragraph{}
During the experiments we saw large differences between the physical and virtual setup. The largest difference is seen on the full-setup.

\paragraph{}
The hardware setup is stable and is functioning quite normal with a responce time of the catalog of 5000ms, but the virtual setup is much more slower with a response of 20.000ms. That is 3 times slower and unacceptable. This might be the effect of distribution transparency.

\paragraph{}
After the experiment with the full application setup we also preformed a test with a webserver only. In this experment with more simple and limited setup we noticed a difference of 5ms between the hardware and VM. In \textbf{figure \ref{fig:resA2hw}}, we see the hardware has an average of 10ms and in \textbf{figure \ref{fig:resA3vm2}} the pure VM has an average delay of 15ms under the same circumstances with the same experiment. We consider that the pure loss of virtualization.

\paragraph{}
In the last test we tried to minimize the difference by optimizing and doubling the CPU and memory assigned to the VM. There was almost no difference visible in performance.

\paragraph{}
We notice that the application performance, in a virtual environment, is strongly affected by the architecture of the application. \par
The webshop has a stateless design where the session date (e.g. shopping-cart) are stored in the datebase. Session related to an session\_id saved in a cookie at the client-side which reffers to a record in the database.